% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass{res} 
\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\setlength{\textheight}{9.5in} % increase text height to fit on 1-page 
\newcommand{\myhrule}{\moveleft\hoffset\vbox{\hrule width\resumewidth}}
\begin{document} 

\name{JAMES PFEIFFER\\[12pt]}     % the \\[12pt] adds a blank
				        % line after name      
\address{http://www.math.washington.edu/\textasciitilde jpfeiff/\\jamesrpfeiffer@gmail.com}
\address{522 North 85th St \#C235\\Seattle, WA 98103\\360-616-1403}


                                  
\begin{resume}

\section{OBJECTIVE}          
    I'm graduating from the UW with a math PhD in December, and I'm looking to
    make a career change into software development due to a love of programming as well as algorithms and math.

\section{EDUCATION} {\sl Mathematics PhD, University of Washington} \hfill (expected) June 2014 \\
                Advisor: Rekha Thomas. Research topics:
                 \begin{itemize}  \itemsep -2pt % reduce space between items
                 \item Semidefinite programming
                \item Sums of squares relaxations and applications
                \item Combinatorial optimization
                \end{itemize}
 
                {\sl Mathematics BS, University of California, Davis} \hfill            June 2009 


\section{EXPERIENCE} {\sl Instructor} \hfill June 2011 - Present\\
                Mathematics Department, University of Washington
                 \begin{itemize}  \itemsep -2pt % reduce space between items
                 \item Taught courses in linear algebra and differential equations.
                \end{itemize}
 
                {\sl Software Intern} \hfill            March - May 2012\\
                Future Advisor (futureadvisor.com)
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                 \item Assisted in implementing a portfolio optimization component for a financial planning website.
                 \end{itemize} 
                {\sl Instructor} \hfill            June - July 2010\\
                Robinson Center, University of Washington
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                 \item Created and taught a discrete mathematics course for gifted middle and high school students.
                 \end{itemize} 
                {\sl Teaching Assistant} \hfill            September 2009 - March 2011\\
                Mathematics Department, University of Washington
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                 \item Led discussion and worksheet sessions for calculus classes.
		\item Held office hours and graded student work.
		\end{itemize}
                {\sl Research Assistant} \hfill            June-August 2007, 2008\\
                Mathematics Department, University of California, Davis
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                 \item Worked with professors and other students on mathematics research.
		\item Tested conjectures via simulations, and implemented proposed algorithms.
                 \end{itemize} 
%                {\sl Teaching Assistant} \hfill            Summers 2006, 2007, 2009\\
%                Center for Talented Youth
%                 \begin{itemize}  \itemsep -2pt %reduce space between items
%                 \item Assisted with math enrichment classes at a summer camp.
%		\item Led nightly discussion/homework sessions.
%                 \end{itemize} 


\section{PUBLICATIONS}
{\em A Semidefinite Approach to the $K_i$ Cover Problem.} J. Gouveia and J. Pfeiffer. Preprint (2012).\\
{\em Bootstrap Percolation on the Hamming Torus.} J. Gravner, C. Hoffman, J. Pfeiffer, and D. Sivakoff. Submitted to Annals of Applied Probability, 2012.


\section{COMPUTER SKILLS}          
    {\em Programming languages:} I use mostly Python now. I appreciate both Lisp and C for their elegance. I have used Ruby, Perl, and C++ as well in the past.

    {\em Software:} Sage (open source math software), MATLAB, Git, Linux, \LaTeX. I've played with webhosting including a Linux server and Google App Engine. 

    {\em Applied theory:} I've used natural language processing and simulated annealing.


 
 
  
 
\end{resume}
\end{document}
